%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Written By Michael Brodskiy
% Class: AP Chemistry
% Professor: J. Morgan
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt]{article} 
\usepackage{alphalph}
\usepackage[utf8]{inputenc}
\usepackage[russian,english]{babel}
\usepackage{titling}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage[super]{nth}
\usepackage{expl3}
\usepackage[version=4]{mhchem}
\usepackage{hpstatement}
\usepackage{rsphrase}
\usepackage{everysel}
\usepackage{ragged2e}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{cancel}
\usepackage{siunitx}
\geometry{top=1.0in,bottom=1.0in,left=1.0in,right=1.0in}
\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%

}
\DeclareSIUnit\Molar{\textsc{m}}
\DeclareSIUnit\atm{\textsc{atm}}
\DeclareSIUnit\torr{\textsc{torr}}
\DeclareSIUnit\psi{\textsc{psi}}
\DeclareSIUnit\bar{\textsc{bar}}
\usepackage{hyperref}
\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,      
urlcolor=blue,
citecolor=blue,
}

\urlstyle{same}


\title{Chapter 5 $-$ Gases}
\date{\today}
\author{Michael Brodskiy\\ \small Instructor: Mr. Morgan}

% Mathematical Operations:

% Sum: $$\sum_{n=a}^{b} f(x) $$
% Integral: $$\int_{lower}^{upper} f(x) dx$$
% Limit: $$\lim_{x\to\infty} f(x)$$

\begin{document}

\maketitle

\begin{itemize}

  \item Gases $-$ Uniformly fill any container; Easily compressed; Mixes completely with other gases; Exert pressure.

  \item Units: $[\si{atm}]=60[\si{\milli\meter}\ce{Hg}]=760[\si{torr}]=14.69[\si{psi}]=1.013[\si{bar}]=101325[\si{\pascal}]$

  \item Boyle's Law $-$ Pressure and volume are inversely related

  \item Charles's Law $-$ Volume directly proportional to temperature

  \item Avogadro's Law $-$ Volume directly proportional to moles

  \item Ideal Gas Law: $PV=nRT$; $R=.0821\left[ \frac{\si{\liter\atm}}{\si{\mole\kelvin}} \right]$

  \item Standard Temperature and Pressure (STP) $-$ $273[\si{\kelvin}]$ and $1[\si{\atm}]$

  \item At STP, one mole of a gas occupies $22.4[\si{\liter}]$

  \item Note: Hydrogen, Nitrogen, Oxygen, and Halogens are diatomics


  \item Gay-Lussac Law $-$ The volume ratio of any two gasses in a reaction at constant pressure and temperature is equal to the mole ratios

  \item The above law means that the type of molecule does not matter, only the amount of molecules. When asked for partial pressure, it may be found using the equation \eqref{1}

    \begin{equation}
      P_{total}=P_a+P_b+\dots+P_n
      \label{1}
    \end{equation}

  \item When asked for the mole fraction, use formula \eqref{2}, where $x_a$ is the mole fraction.

    \begin{equation}
      P_a=x_aP_{total}
      \label{2}
    \end{equation}
    

  \item Kinetic Molecular Theory $-$ Gases are made of small particles in constant, random motion. Collisions with wall cause pressure. Kinetic energy is directly proportional to temperature. If Temperature $\up$ then average speed $\up$ pressure $\up$, etc.

  \item Speed $-$ $U=\left( \frac{3RT}{M} \right)^{\frac{1}{2}}$

  \item Effusion $-$ Flow of gas particles through tiny hole. Smaller molar mass particles effuse faster. Graham's Law.

  \item $\frac{U_b}{U_a}=\left( \sqrt{\frac{m_{molar_a}}{m_{molar_b}}} \right)$

    \begin{equation}
      m_{molar}=\frac{g}{V}\cdot\frac{RT}{P}
      \label{3}
    \end{equation}

  \item Non-Ideal Conditions $-$ At these conditions, gases act less ideal:

    \begin{enumerate}

      \item Low Temperatures $-$ Particles slow down, attractive forces take over. Observed volume is less than calculated.

      \item High Pressures $-$ Particles are pushed together, attractive forces take over. Observed volume is less than calculated.

      \item Very High Pressures $-$ Size of particles prevent volume from getting smaller. Observed volume is greater than calculated.

    \end{enumerate}

\end{itemize}

\end{document}

