%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Written By Michael Brodskiy
% Class: AP Language & Composition
% Professor: J. Greer
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt]{article} 
\usepackage{alphalph}
\usepackage[utf8]{inputenc}
\usepackage[russian,english]{babel}
\usepackage{titling}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage[super]{nth}
\usepackage{everysel}
\usepackage{ragged2e}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{cancel}
\usepackage{siunitx}
\usepackage{xcolor}
\geometry{top=1.0in,bottom=1.0in,left=1.0in,right=1.0in}
\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%

}
\usepackage{hyperref}
\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,      
urlcolor=blue,
citecolor=blue,
}

\urlstyle{same}


\title{Comparisons}
\date{February 4, 2021}
\author{Michael Brodskiy\\ \small Instructor: Mrs. Greer}

% Mathematical Operations:

% Sum: $$\sum_{n=a}^{b} f(x) $$
% Integral: $$\int_{lower}^{upper} f(x) dx$$
% Limit: $$\lim_{x\to\infty} f(x)$$

\begin{document}

    \maketitle

    \begin{enumerate}

        \begin{center}
          Fix the comparison error, if necessary
        \end{center}

      \item The ship could not maneuver effectively because too \cancel{much} \underline{many} barrels of provisions and cases of ammunition had been stored on board.

      \item In nineteenth-century America, activists such as Elizabeth Cady Stanton and Susan B. Anthony urged women to become \cancel{a participant} \underline{participants} in the democratic process.

      \item The world problem asked students to determine the amount of marbles that could fill a cylindrical jar. \textcolor{green}{\textsc{correct}}

      \item He believes that wearing sandals in summer is better for his heath than \underline{wearing} sneakers.

      \item Senator Joseph McCarthy rose to notoriety by determining which citizens of the United States had \cancel{a} communist belief\underline{s}. 

      \item Terry is firmly convinced that the best comic novels are P.D. Wodehouse. \textcolor{green}{\textsc{correct}}

      \item After much deliberation, the judges decided that Grover was the \cancel{better} \underline{best} of the seven performers who had appeared in the talent show.

      \item It is hard to deny that flying in a private jet is a much more glamorous way to travel than \underline{flying in} a commercial plane.

      \item Only a few of the air force cadets were interested in becoming astronauts. \textcolor{green}{\textsc{correct}}

      \item Like so many other academic essays on literature, Sharon bombards readers with awkward sentences and unclear definitions. \textcolor{green}{\textsc{correct}}

      \item The gardening and yard maintenance duties were equally divided \cancel{between} \underline{among} Jacques, Frank, and me.

      \item Perseverance and determination are among many skills that will lead you to success in your college studies. \textcolor{green}{\textsc{correct}}

        \begin{center}
          Choose the correct option
        \end{center}

        \setcounter{enumi}{0}

      \item B

      \item C

      \item B

      \item D

      \item A

      \item B

      \item C

      \item C

    \end{enumerate}

\end{document}

