\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{ragged2e}
\usepackage[colorlinks = true,
            linkcolor = purple,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,} 
\urlstyle{same}


\usepackage{ifpdf}
\usepackage{mla}

\begin{document}

\begin{mla}{Michael}{Brodskiy}{Mrs. Greer}{AP Language}{\today}{\underline{The Memoirs of George Washington}} 

  \begin{justifying}

    \paragraph{} In \emph{George Washington and Mount Vernon}, George Washington presents his public nature as the inaugural president of a newly found American Republic. Washington conveys his impeccable mastery of political aptitude without the unnecessary fraternization with colleagues and admirers all the while displaying compassion and interest in their business or any other causes. The implicit connotation of the text assumes that Washington was a man of unsurpassed conviction and honor of the highest decree; the ultimate paradigm of man to hold public office. His accomplishments speak for themselves, and, considered in tandem with his uncanny ability to win people over rhetorically, as evident in his eloquent address aimed at the audiences of his letters, it can be concluded that he really was a selfless ruler of the newly found American Republic. In the text, Washington is presented in a new light, depicting him as an exemplary world leader. Later on in the text Washington examines his achievements as a military man within the backdrop of the American Revolution. This reminiscing sheds light on a whole new Washington, a Washington capable of engaging with the enemy in an uncompromising capacity while performing numerous intelligence operations to secure the independence of himself and his fellow countrymen. As such, the memoirs of George Washington demonstrate that, in addition to being an eloquent and captivating speaker and writer, Washington was a more than competent leader; therefore, these two skills encapsulate Washington's qualifications to lead his country.
      
\end{justifying}
\centering Word Count: 250

\end{mla}

\end{document}

