%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Written By Michael Brodskiy
% Class: AP Language & Composition
% Professor: J. Greer
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt]{article} 
\usepackage{alphalph}
\usepackage[utf8]{inputenc}
\usepackage[russian,english]{babel}
\usepackage{titling}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage[super]{nth}
\usepackage{everysel}
\usepackage{ragged2e}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{cancel}
\usepackage{siunitx}
\usepackage{xcolor}
\geometry{top=1.0in,bottom=1.0in,left=1.0in,right=1.0in}
\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%

}
\usepackage{hyperref}
\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,      
urlcolor=blue,
citecolor=blue,
}

\urlstyle{same}


\title{Parallelism}
\date{January 28, 2021}
\author{Michael Brodskiy\\ \small Instructor: Mrs. Greer}

% Mathematical Operations:

% Sum: $$\sum_{n=a}^{b} f(x) $$
% Integral: $$\int_{lower}^{upper} f(x) dx$$
% Limit: $$\lim_{x\to\infty} f(x)$$

\begin{document}

    \maketitle

    \begin{enumerate}

        \begin{center}
          Balance the sentence, if necessary
        \end{center}

      \item In preparation for the train heist, the outlaws obtained ropes and ladders, disguised themselves in black clothing, and \cancel{then also} devised a foolproof escape plan.

      \item If you are interested in learning about Italian cinema, \cancel{one} \underline{you} should watch the film \textit{La Strada}.

      \item The ballerina was neither committed to a single performance style nor was she willing to ally herself with only one dance troop. \textcolor{green}{\textsc{correct}}

      \item Many students would agree that actually traveling the world is more exciting than \cancel{when you simply read} \underline{simply reading} about faraway places.

      \item In recent times, some investment bankers have been more interested in amassing wealth than in \cancel{how} \underline{following} scrupulous \cancel{the} business practices \cancel{they follow are}.

      \item To say that Meredith works out ``now and then'' is \cancel{underestimating} \undeline{to underestimate} her devotion to health and fitness.

      \item Norman yearned not only to write innovative poetry, but also he yearned to create experimental sculptures and architectural designs. \textcolor{green}{\textsc{correct}}

      \item Walking through the old house was like \cancel{a return} \underline{returning} to all my childhood fears.

      \item The Caribbean heritage festival attracted traditional dancers, community service organizers, and documentaries by directors from around the world. \textcolor{green}{\textsc{correct}}

      \item Richard is worried not only about how his teachers perceive him, but also about \underline{how} his peers \cancel{reacting} \underline{react} to his personality.

      \item Delilah prefers the music of the Rolling Stones to the music \cancel{which was made by} \underline{of} the Beatles.

      \item Visitors discovered that the performance art exhibit was not only innovative, but also \cancel{it educated} \underline{educative}.

      \item My uncle purchased steaks and sausage links, set up his new deck furniture, and \cancel{he also} sent out invitations for his Friday cookout.

      \item Compared to its competitors, the new bistro is more spacious and \cancel{it is} more efficiently managed.

      \item Linda is neither comfortable speaking in front of others nor \cancel{is she} capable of making her points succinctly.

        \begin{center}
          Answer the following questions using one of the options given
        \end{center}

        \setcounter{enumi}{0}

      \item D

      \item C

      \item B

      \item B

      \item C

    \end{enumerate}

\end{document}

