%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Written By Michael Brodskiy
% Class: AP Language & Composition
% Professor: J. Greer
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt]{article} 
\usepackage{alphalph}
\usepackage[utf8]{inputenc}
\usepackage[russian,english]{babel}
\usepackage{titling}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage[super]{nth}
\usepackage{everysel}
\usepackage{ragged2e}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{cancel}
\usepackage{siunitx}
\geometry{top=1.0in,bottom=1.0in,left=1.0in,right=1.0in}
\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%

}
\usepackage{hyperref}
\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,      
urlcolor=blue,
citecolor=blue,
}

\urlstyle{same}


\title{Subject Verb Agreement}
\date{January 21, 2021}
\author{Michael Brodskiy\\ \small Instructor: Mrs. Greer}

% Mathematical Operations:

% Sum: $$\sum_{n=a}^{b} f(x) $$
% Integral: $$\int_{lower}^{upper} f(x) dx$$
% Limit: $$\lim_{x\to\infty} f(x)$$

\begin{document}

    \maketitle

    \begin{enumerate}

        \begin{center}
          Fix the verb(s) where necessary:
        \end{center}

      \item By Anita's estimate, there \cancel{is} \underline{are} at least a hundred birds in the tropical rain forest exhibit.

      \item There \cancel{has} \underline{have} always been too many conflicting clauses and stipulations in the company's hiring policy.

      \item There \cancel{is} \underline{was} a public park, a swimming pool, and a miniature golf course just down the road from the house where I grew up. (\textit{Alternatively, switch \underline{grew} to \underline{am growing}})

      \item The principles of morality, government, and perception \cancel{was} \underline{were} all investigated by British philosopher John Locke.

      \item Neither Mr. Carruthers nor his son \cancel{were} \underline{was} invited to this year's golf outing.

      \item Neither one of the contestants \cancel{were} \underline{was} willing to use dishonest methods and thus risk her reputation.

      \item The overwhelming support of both emerging and established authors \cancel{have} \underline{has} undeniably enriched the world literature scene.

      \item The proceeds from the auction of Ms. Dutton's estate \cancel{was} \underline{were} distributed among her children.

      \item Neither the cheerleaders nor the football players themselves \cancel{believes} \underline{believe} that the coach has had a positive influence on the team.

      \item Either a German novel or a French novel \cancel{are} \underline{is} going to be assigned to the class for summer reading.

      \item There \cancel{is} \underline{are} five more miles to go until we reach our destination.

      \item Weather phenomena, from deadly tornadoes to gentle spring rain, \cancel{is} \underline{are} analyzed in great detail on an informative new television show.

      \item The building inspectors were astonished to discover that there \cancel{was} \underline{were} three hidden rooms in the basement of the old mansion.

      \item Every tenured faculty member of the department of literature and languages \cancel{were} \underline{was} present at Dr. McNulty's retirement party.

        \begin{center}
          Practice Multiple Choice:
        \end{center}

        \setcounter{enumi}{0}

      \item B) there are

      \item D) is

      \item B) This is

      \item C) seem

      \item D) are

      \item B) makes

      \item A) NO CHANGE

    \end{enumerate}

\end{document}

