\documentclass[a4paper]{article} 
\usepackage{tcolorbox}
\tcbuselibrary{skins}

\title{
\vspace{-3em}
\begin{tcolorbox}[colframe=white,opacityback=0]
\begin{tcolorbox}
\Huge\sffamily\centering Synthesis Prompt Notes
\end{tcolorbox}
\end{tcolorbox}
\vspace{-3em}
}

\date{}

\usepackage{background}
\SetBgScale{1}
\SetBgAngle{0}
\SetBgColor{grey}
\SetBgContents{\rule[0em]{4pt}{\textheight}}
\SetBgHshift{-2.3cm}
\SetBgVshift{0cm}

\usepackage{lipsum}% just to generate filler text for the example
\usepackage[margin=2cm]{geometry}

\usepackage{tikz}
\usepackage{tikzpagenodes}

\parindent=0pt

\usepackage{xparse}
\DeclareDocumentCommand\topic{ m m g g g g g}
{
\begin{tcolorbox}[sidebyside,sidebyside align=top,opacityframe=0,opacityback=0,opacitybacktitle=0, opacitytext=1,lefthand width=.3\textwidth]
\begin{tcolorbox}[colback=red!05,colframe=red!25,sidebyside align=top,width=\textwidth,before skip=0pt]
#1\end{tcolorbox}%
\tcblower
\begin{tcolorbox}[colback=blue!05,colframe=blue!10,width=\textwidth,before skip=0pt]
#2
\end{tcolorbox}
\IfNoValueF {#3}{
\begin{tcolorbox}[colback=blue!05,colframe=blue!10,width=\textwidth]
#3
\end{tcolorbox}
}
\IfNoValueF {#4}{
\begin{tcolorbox}[colback=blue!05,colframe=blue!10,width=\textwidth]
#4
\end{tcolorbox}
}
\IfNoValueF {#5}{
\begin{tcolorbox}[colback=blue!05,colframe=blue!10,width=\textwidth]
#5
\end{tcolorbox}
}
\IfNoValueF {#6}{
\begin{tcolorbox}[colback=blue!05,colframe=blue!10,width=\textwidth]
#6
\end{tcolorbox}
}
\IfNoValueF {#7}{
\begin{tcolorbox}[colback=blue!05,colframe=blue!10,width=\textwidth]
#7
\end{tcolorbox}
}
\end{tcolorbox}
}

\def\summary#1{
\begin{tikzpicture}[overlay,remember picture,inner sep=0pt, outer sep=0pt]
\node[anchor=south,yshift=-1ex] at (current page text area.south) {% 
\begin{minipage}{\textwidth}%%%%
\begin{tcolorbox}[colframe=white,opacityback=0]
\begin{tcolorbox}[enhanced,colframe=black,fonttitle=\large\bfseries\sffamily,sidebyside=true, nobeforeafter,before=\vfil,after=\vfil,colupper=black,sidebyside align=top, lefthand width=.95\textwidth,opacitybacktitle=1, opacitytext=1,
segmentation style={black!55,solid,opacity=0,line width=3pt},
title=Summary
]
#1
\end{tcolorbox}
\end{tcolorbox}
\end{minipage}
};
\end{tikzpicture}
}

\usepackage{graphicx}
\usepackage{physics}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{mathdots}
\usepackage{yhmath}
\usepackage{cancel}
\usepackage{color}
\usepackage{siunitx}
\usepackage{array}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{hyperref}
\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,      
urlcolor=blue,
citecolor=blue,
}
\urlstyle{same}
\usetikzlibrary{fadings}
\usetikzlibrary{patterns}
\usetikzlibrary{shadows.blur}
\usetikzlibrary{shapes}\usepackage{fancyhdr}
\pagestyle{fancy}
\lfoot[\vspace{-15pt} \hline]{\vspace{-15pt} \hline}
\rfoot[\vspace{-15pt} \hline]{\vspace{-15pt} \hline}
\cfoot[\thepage]{\thepage}
\lhead[\copyright 2021 $-$ \textit{All Rights Reserved} ]{\copyright 2021 $-$ \textit{All Rights Reserved}}
\chead[AP Language and Composition]{AP Language and Composition}
\rhead[Michael Brodskiy]{Michael Brodskiy}


\begin{document} 
\maketitle

\topic{Stable Language}{Read the six sources, including introductory information for each source. }
  {Then, write an essay that synthesizes at least three of the sources and develops your position on the topic you are asked to address.}%
    
\topic{Timing}{There are fifteen minutes to read the prompt and sources, and forty minutes total for the essay.} 
{It is recommended to look at those sources during those first fifteen minutes.}%
    
\topic{Goals of the Synthesis Prompt}{Critical Reading}
{Focused Argument}
{Organization}
{Use of Source Material}
{Citation of Source Material}%
    
\topic{Who is supposed to be in control?}{Show you are in control of the sources. Use them to guide your argument, not define it.}
{Try to pair sources to make writing easier.}%
    
\topic{Public Libraries}{You are invited to ``develop a position on the role, if any, that public libraries should serve in the future.''}
{Sources given vary from blogs and more traditional articles to activity calendars, bar graphs depicting e-book use, and librarian assistance to patrons.}%
    
\topic{Monuments}{This one uses language that doesn't comport with the new promised language, so adjustments were made.}
{Here, you're invited to take a position on ``the factors a group or agency should consider in memorializing an event or person and in creating a monument''}%
    
\topic{Wind Farms}{When it comes to energy, wind farms may not be the first thing that comes to mind.}
{This 2019 prompt asks, ``develop your position on the most important factors that an individual or agency should consider when deciding whether to establish a wind farm''}
{It is suggested to always try to use charts or graphs, when given.}%
    
\topic{The USPS}{The 2012 prompt states, ``take a position on whether the USPS should restructured to meet the needs of a changing world, and if so, how''}
{Unlike other prompts, this one also asks for solutions for the future.}
{Example Thesis: \textit{The United States Postal Service should continue to adapt to the ongoing needs and demands of changing communication and commerce, embracing emerging delivery methods}}%
    
\topic{Skills}{All of the skills learned in the class will continue to build on each other, including the ability to synthesize documents.}%
    
\topic{Citations}{Be very careful of citing anything, including someone in a class discussion.}%
    
%\topic{Here's another question to begin the new page.}{\lipsum[3]}%
%{\lipsum[4]}%
%{\lipsum[5]}%

%\summary{And another summary that will float to the bottom of the next page.}

\end{document}
