%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Written By Michael Brodskiy
% Class: AP English Literature & Composition
% Instructor: Mr. Cautero
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt]{article} 
\usepackage{alphalph}
\usepackage[utf8]{inputenc}
\usepackage[russian,english]{babel}
\usepackage{titling}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{physics}
\usepackage{tikz}
\usepackage{mathdots}
\usepackage{yhmath}
\usepackage{cancel}
\usepackage{color}
\usepackage{siunitx}
\usepackage{array}
\usepackage{multirow}
\usepackage{gensymb}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{soul}
\usetikzlibrary{fadings}
\usetikzlibrary{patterns}
\usetikzlibrary{shadows.blur}
\usetikzlibrary{shapes}
\usepackage[super]{nth}
\usepackage{expl3}
\usepackage[version=4]{mhchem}
\usepackage{hpstatement}
\usepackage{rsphrase}
\usepackage{everysel}
\usepackage{ragged2e}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{cancel}
\geometry{top=1.0in,bottom=1.0in,left=1.0in,right=1.0in}
\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%

}
\usepackage{hyperref}
\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,      
urlcolor=blue,
citecolor=blue,
}

\urlstyle{same}


\title{“The First Michael Jordan” Analysis}
\date{\today $-$ Period 5}
\author{Michael Brodskiy\\ \small Instructor: Mr. Cautero}

% Mathematical Operations:

% Sum: $$\sum_{n=a}^{b} f(x) $$
% Integral: $$\int_{lower}^{upper} f(x) dx$$
% Limit: $$\lim_{x\to\infty} f(x)$$

\begin{document}

\maketitle

\begin{enumerate}

  \item What is Will's attitude toward DiMaggio

    Through the use of words like “burst” and “aura”, it is indicated that Will looks up to DiMaggio as an exemplary figure or celebrity

  \item \begin{tabular}{|c|c|c|c|} \hline \textbf{Diction} & \textbf{Detail} & \textbf{Imagery} & \textbf{Syntax} \\ \hline burst & rough-and-tumble & aura & interruption (“- of a kind, really -“)\\ \hline invented & leveling & celebrity & quote is two sentences \\ \hline an artist & remoteness & Lindbergh & \\ \hline intuitive & never before experienced & & \\ \hline \end{tabular}

  \item Commentary:

    In the quotation, George F. Will conveys a tone of admiration towards DiMaggio, as he describes the celebrity's appearance. This tone is developed through the use of specific diction and colorful details that promote the god-like respect Will holds for DiMaggio. For example, Will states that DiMaggio “burst upon the nation”. This portrays a grand entrance, signaling that this entrance holds special significance; thus, it is indicated that DiMaggio was like none other before him. Additionally, Will details DiMaggio's appearance as “never before experienced”. This makes DiMaggio seem more unique, as no one prior to DiMaggio's time was able to make such a grand celebrity of oneself. As such, it is evident that Will looks up to DiMaggio, both as an artist and a revolutionary performer.

\end{enumerate}

\end{document}

