%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Written By Michael Brodskiy
% Class: AP Macroeconomics
% Instructor: Mr. Bremer
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt]{article} 
\usepackage{alphalph}
\usepackage[utf8]{inputenc}
\usepackage[russian,english]{babel}
\usepackage{titling}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{physics}
\usepackage{tikz}
\usepackage{mathdots}
\usepackage{yhmath}
\usepackage{cancel}
\usepackage{color}
\usepackage{siunitx}
\usepackage{array}
\usepackage{multirow}
\usepackage{gensymb}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{soul}
\usepackage{multicol}
\usepackage{pgfplots}
\pgfplotsset{compat=newest}
\usetikzlibrary{fadings}
\usetikzlibrary{patterns}
\usetikzlibrary{shadows.blur}
\usetikzlibrary{shapes}
\usepackage[super]{nth}
\usepackage{expl3}
\usepackage[version=4]{mhchem}
\usepackage{hpstatement}
\usepackage{rsphrase}
\usepackage{everysel}
\usepackage{ragged2e}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{cancel}
\geometry{top=1.0in,bottom=1.0in,left=1.0in,right=1.0in}
\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%

}
\usepackage{hyperref}
\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,      
urlcolor=blue,
citecolor=blue,
}

\urlstyle{same}


\title{Bremerisms (2021$-$2022)}
\date{Period 3}
\author{Michael Brodskiy\\ \small Instructor: Mr. Bremer}

\begin{document}

\maketitle

\begin{enumerate}

  \item “Hey, your mom is coming over to my house tonight” — September 2, 2021

  \item “Now, I don't know why that is. I'm not smart enough at math to figure that out, but I know it is between those values.” — September 20, 2021

  \item ``It's like an avocado — it's got to be soft, but not \textit{too} soft'' — September 23, 2021

  \item ``You know, I tried to learn Spanish a few years ago — English is much worse — but when it came to congregations-congreg-conju-conjugations, I gave up'' — September 23, 2021

  \item ``It was March 5, 1982. I had my first date. Yep. Don't do what I did. I took her to see a movie. It was a forgettable film called \textit{Dead Men Don't Wear Plaid}'' — September 23, 2021

  \item *\textit{Draws $P$ and $Q$ on hands}* ``It's because price and quantity go up'' *\textit{raises both hands}* ``so we need to hold price constant'' *\textit{raises quantity hand}* — September 23, 2021

  \item ``You know what, I'll be a poopy pants'' — September 23, 2021

  \item “If someone has a, you know, \textit{bear in the cave}, you have to tell them. You need to. They'll appreciate it.” — September 27, 2021

  \item “Am I \textit{that} good at describing this? Yeah, I guess I am” — September 27, 2021

  \item *\textit{Taps aggressively while staring at a USS Arizona poster}* — September 28, 2021

  \item “Look at that ascendance. Love it. ” — September 28, 2021

  \item “Hey, *bucks cheese and crackers!” *\textit{reaches into trash}* “Now, I'm gluten free so I can't have it. Does anybody want these?” — September 30, 2021

  \item “Look, I'm gonna be honest. When I walk by the dumpsters, if no one were around, I would grab the food. Have you seen some of the stuff they throw out? It's beautiful” — September 30, 2021

  \item “Can someone stop banging? Who is the banger?” — September 30, 2021

  \item “Well, if you tell me your dog died \dots I have \textit{some} compassion” — October 18, 2021

  \item “I started here in 1997. There were four of those chairs in the library. They date back to the 1960s. The chairs were so in demand that the librarian wanted to get rid of them. I took one of them. The other three are gone. Every year, I take it to the auto shop to clean off all of the dead skin cells. Anyway, that's the chair story.” — October 21, 2021

  \item “I ran into Mrs. Amin once. I said 'Hi Ladan!' She said 'I haven't got a clue.'” — October 21, 2021 

  \item “I took physics a long time ago. What is it? 2.6? 4.3? meters per second per second. Oh, well I was close.” — October 25, 2021

  \item “Have I told this class of my sinus infection?” — October 26, 2021

  \item “You should teach Mr. Cautero about economics so he learns something about the real world” — October 27, 2021


  \item “Now, if your dog dies, you have to deal with it” — January 6, 2022

  \item “That's like the corner of death. I don't want to put a student there unless I have to.” — February 1, 2022

  \item ``If a bottle of heroin were, say, here. It would be harmless unless ingested \dots I wouldn't know, I'm not a heroin guy'' — February 1, 2022

  \item “I'd like to have a curve named after me” — February 3, 2022

  \item “That's all I need \dots vibrations in my head” — February 3, 2022

  \item “Has anyone here, as a child, ever had a fear of elevator doors closing in on you?” — February 3, 2022

  \item “I don't have curtains like that. I'm a member of the proletariat” — February 3, 2022

  \item “It's a trauma associated with elevators doors \dots I should probably talk to someone about that” — February 3, 2022

  \item “His mom shows up every now and then with a large group of women” — February 7, 2022

  \item “You can't just get more land \dots well, maybe if you're Vladimir Putin you can” — February 8, 2022

  \item *\textit{Staring at projector slowly turning on}* \textit{sigh} “yep” — March 10, 2022

  \item *\textit{Stares at water bottle slowly rolling towards feet}* “Wow. It's fortuitous it rolled right towards me” — March 10, 2022

  \item “Someone said `that shit hits' \dots I'm going to assume that means it is very delicious” — March 10, 2022

  \item “Alright, we'll just wait for the Bradshites to alive” — April 19, 2022

  \item “Please, no emanations from your gullet” — April 19, 2022

  \item “I'm going to re-rase this” — April 19, 2022

  \item “Tupac — well, Tupac's not dead. He's living in Modesto” — April 19, 2022

  \item *\textit{Phone rings loudly}* “Sorry, it's my mom, I gotta take it. Wait, not it's not. I don't.” — April 19, 2022

  \item “People aren't dumb. Well, most aren't.” — April 19, 2022

  \item “It made me want to smash my head against that table there. Violently. Not your head, my head.” — April 26, 2022
    
\end{enumerate}

\end{document}

