\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{ragged2e}
\usepackage[colorlinks = true,
            linkcolor = purple,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,} 
\urlstyle{same}


\usepackage{ifpdf}
\usepackage{mla}

\begin{document}

\begin{mla}{Michael}{Brodskiy}{Mrs. Greer}{AP Language}{March 23, 2021}{\underline{Should Nick and Cathy Date?}} 

  \begin{justify}

    \paragraph{} Through analysis of the provided sources, it is evident that Nick and Cathy should cease their romantic relationship, as it seems the two are not mutually fascinated, as Nick commonly cancels last minute on plans with Cathy, usually to meet with other girls with whom he seems very close, while Cathy still has feelings for her former boyfriend.

  \end{justify}

  \begin{justify}

    \paragraph{} It is clear that Nick constantly makes plans with other girls, usually Amanda, which causes him to cancel plans with his girlfriend, Cathy. Nick and Cathy have a discussion via SMS messaging that portrays a conversation in which it becomes clear that Nick has canceled ``almost last-minute'' (Source B, Text Messages). In the same source, one must pay close attention to the date, which is a Friday. Analyzing this in tandem with Nick and Cathy's respective daily schedules (Source A), it becomes clear that Cathy migrated her work time to the weekend to spend time with Nick, who does not seem to respect her time. Albeit canceling plans to spend time with another girl is already unprincipled, the situation is exacerbated by the fact that Cathy took the night off to spend time with Nick. In this manner, it is clear that Nick does not have respect for Cathy or her time, and, therefore, the two should not be together.

  \end{justify}

  \begin{justify}

    \paragraph{} On top of not respecting Cathy, Nick is close with the other girl he usually spends time with, Amanda. Although the argument may be made that Nick was constantly texting Cathy through the night that he canceled the plans, and even called her before bed (Source B), this only describes that single night and not the other times he has been with Amanda, as Cathy says that this is his ``3rd or 4th time'' canceling. On top of this, Amanda's Instagram (Source F) only aggravates the issue, as the image presented demonstrates Nick and Amanda making frivolous faces in a picture of the two, where they are very close together, and may be perceived as a couple. Amanda's caption also states that Nick is her ``fav guy'', which makes the relationship between the two suspicious at best. As such, it is clear that Nick's morality is beset by licentiousness and turpitude, which only adds to the fact that the two should not be a couple. 

  \end{justify}

  \begin{justify}

    \paragraph{} Although Nick's unscrupulous behavior is reason enough to terminate the relationship, it seems as though Cathy herself is interested in another person as well. Statements from Friends and Classmates (Source C) describe that ``Cathy has feelings for her ex-boyfriend Jake''. If the assumption is made that this statement is true (as it was provided by an untrustworthy and gossiping source named Danielle), then it almost seems as though discontinuing this relationship would be mutually beneficial. With this in mind, it is almost an absolute that the two should stop dating.

  \end{justify}

  \begin{justify}

    \paragraph{} Overall, it is clear that the two are not fit for each other. Not only do both Nick and Cathy have other friends with whom it seems they could have romantic relationships, but also it seems that the two do not care for each other in general. Following this path, it seems only logical that the two should terminate their romantic relationship, although they could continue with a platonic one.

  \end{justify}


\end{mla}

\end{document}

