\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[english]{babel}
\usepackage{lipsum}
\usepackage{comment}

\usepackage{hyperref}
\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,      
urlcolor=blue,
citecolor=blue,
}

\urlstyle{same}

\usepackage[
 backend=biber,
 bibstyle=numeric,
 style=numeric,
 sorting=nty,
 hyperref=true,
 %citestyle=mla
]{biblatex}
\addbibresource{sources.bib}

\title{Self-Assessment for Careers}
\author{Full Name: \textsc{Michael Brodskiy}}
\date{March 23, 2020}

\begin{document}

\maketitle

\begin{enumerate}

    \item What is the overall field for the career in which you are interested?\\
         \vspace{5pt}
         Engineering

    \item What is the specific career you would like to research? \\
        \vspace{5pt}
        Nuclear Physicist \& Engineer

    \item The nature of the work $-$ What specific activities or tasks does a person in this job typically have to do on a daily basis? \\
        \vspace{5pt}
        
        "Nuclear physicists study the way atoms interact with each other, as well as how the characteristics of the nuclear world can be applied to human endeavors. Nuclear physicists may focus on one of several subspecialties including theoretical work, experimental examinations of nuclear particles and equipment design." The most concise way to describe a Nuclear Physicist's work is as follows: a Nuclear Physicist takes known theories, both scientific and mathematical, and applies those theories, possibly in conjunction with his or her own, to expand the field of Nuclear Science.

    \item Cite The Source: \\
        \vspace{5pt}
        \cite{workNature:1}\footnote{You can click on citations to go to them}

\newpage
        
    \item Working conditions – This refers to such things as the type of work environment, the location of the work, and the physical requirements of the job.\\\\
    \vspace{5pt}
    \vspace{5pt}
    \begin{tabular}{l l}
    $\blacksquare$ & Indoors\\
    $\square$ & Outdoors\\
    $\square$ & Combination of indoors and outdoors\\
    $\square$ & Work alone\\
    $\blacksquare$ & Work as part of a team\\
    $\square$ & Combination of alone and as part of a team\\
    $\blacksquare$ & Travel\\
    $\square$ & No travel\\
    $\square$ & Primarily standing\\
    $\square$ & Primarily sitting\\
    $\blacksquare$ & Combination of sitting and standing\\
    $\blacksquare$ & Computer work\\
    
   
    
\end{tabular}

    \item Cite The Source: \\
        \vspace{5pt}
        \cite{workNature:1}

    \item Where would a person in this career most likely be employed?\\\\
    \vspace{5pt}
    \vspace{5pt}
    \begin{tabular}{l l}
    $\blacksquare$ & Private, small business/office\\
    $\square$ & Public, large corporation/business/office\\
    $\blacksquare$ & Public institution\\
    $\blacksquare$ & Government Agency\\
    $\square$ & Large cities\\
    $\square$ & Any town or city\\
    $\blacksquare$ & Specific cities\\
    $\blacksquare$ & May rotate within the United States or overseas, as needed.\\
    $\blacksquare$ & Other \underline{Power Plant}\\
    
    \end{tabular}
    
    \item Cite The Source: \\
        \vspace{5pt}
        \cite{workNature:1}

   \item Necessary education for this position $-$ Would a candidate for this career need a degree? Or, does the career call for specialty vocational training?\\
     \vspace{5pt}
    \vspace{5pt}
    \begin{tabular}{l l}
    $\circ$ & Associate's Degree\\
    $\circ$ & Bachelor's Degree\\
    $\circ$ & Master's Degree\\
    $\bullet$ & Doctoral Degree/Doctorate\\
    $\circ$ & Specialty Vocational Training and Certificate\\
    $\circ$ & Military Training\\
    $\circ$ & Other:\\
    \end{tabular}
    
    \item \textsc{In addition to a degree/training}, would this career require a special certification or a credential?\\
    \vspace{5pt}
    \vspace{5pt}
    \begin{tabular}{l l}
    $\circ$ & Certification\\
    $\circ$ & Credential\\
    $\circ$ & License\\
    $\bullet$ & No certification, credential, or license required\\
    $\circ$ & Other:\\
    \end{tabular}
    
    \item Would you have to pass any state licensing tests, such as a state Bar Exam for lawyers?\\
    \vspace{5pt}
    \vspace{5pt}
    \begin{tabular}{l l}
    $\square$ & State Test required\\
    $\square$ & Internship required\\
    $\square$ & Residency required\\
    $\square$ & Apprenticeship required\\
    $\blacksquare$ & None of these appear to be necessary\\
    $\blacksquare$ & Other: Clearance, if in a government position\\
    \end{tabular}
    
    \item Cite The Source: \\
    \vspace{5pt}
    \cite{educReq}
    
    \item What is the annual, median salary for this particular career?
    \$107,600
    
    \item Cite The Source: \\
    \vspace{5pt}
    \cite{oneStop}
    
    \item According to the Occupational Outlook Handbook, what is the career outlook (projected growth) for this career 10 years from now?
    -1\%
    
    \item Cite The Source: \\
    \vspace{5pt}
    \cite{oneStop}
    
    \item What special skills, knowledge, or abilities will a person in this career be expected to have?
    Knowledge of Analytical Geometry and Calculus in a 3 Dimensional Field, Ability to use computer mathematical-based software to run simulations, and extensive knowledge of atomic physics and fluid mechanics.
    
    \item Cite The Source: \\
    \vspace{5pt}
    \cite{workNature:1}
    
    \item Additional Information\\
    None
    
    \item Cite the Source:
    None
    
\end{enumerate}

\printbibliography

\end{document}
