\documentclass[12pt]{article} 

\usepackage[utf8]{inputenc}
\usepackage[russian]{babel}
\usepackage{titling}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage[super]{nth}
\usepackage{everysel}
\usepackage{ragged2e}
\usepackage{geometry}
\geometry{top=1.0in,bottom=1.0in,left=1.0in,right=1.0in}
\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%
}
\renewcommand*\familydefault{\ttdefault}
\EverySelectfont{%
\fontdimen2\font=0.4em% interword space
\fontdimen3\font=0.2em% interword stretch
\fontdimen4\font=0.1em% interword shrink
\fontdimen7\font=0.1em% extra space
\hyphenchar\font=`\-% to allow hyphenation
}

\begin{document}

%------------------------------------------------------------------------------------------
% Title
%------------------------------------------------------------------------------------------

\author{Michael \textsc{Brodskiy}}
\title{Defining Chapter 30 \\European History AP}
\subtitle{Mrs Fisher}
\date{March 23, 2020}
\maketitle

%------------------------------------------------------------------------------------------
% Questions
%------------------------------------------------------------------------------------------

\begin{flushleft}
\begin{enumerate}

	\item \textbf{Big Three} $-$ The Big Three was used to refer to the three main leaders of nations during the Second World War. These were Joseph Stalin, Franklin Roosevelt, and Winston Churchill.

	\item \textbf{Tehran} $-$ A conference was held in Tehran in 1943. Here, the Big Three met in order to discuss how they planned to finish the war, and their hopes afterward. This would be the first major meeting in which post-war plans were discussed.

    \item \textbf{Yalta} $-$ Much alike the Tehran Conference of 1943, the Yalta Conference was held in order to make important post-war decisions. It took place from the \nth{4} to \nth{11} of February in 1945, at a point when it was evident that the Soviets would reach Berlin before the allied forces. The schism between the allies would first appear at this conference, and it would become evident that the three would be unable to coexist peacefully. The major decisions included the decisions on the reorganization of Europe.

    \item \textbf{Potsdam} $-$ The main discussion at the post-war Potsdam Conference, which lasted from the \nth{17} of July to the \nth{2} of August in 1945, would revolve around what was to be done with Germany. The majority of any post-war treaties and orders would be established here. Stalin had decided that he wanted many Eastern-European states as buffers from the west. This would enrage Churchill. This conference, however, would have Truman attend instead of Roosevelt.

    \item \textbf{Iron Curtain} $-$ The ``\emph{Iron Curtain}''  was a metaphor from Winston Churchill regarding the censorship present in the Soviet Union and satellite states.

	\item \textbf{Truman Doctrine} $-$ The Truman Doctrine was Harry Truman's policy towards countries that would possibly turn communist. He would supply military and financial aid to these countries.

	\item \textbf{Marshall Plan} $-$ The Marshall Plan was intended to recover the failing economies of European states. No countries were excluded from this, however, the Soviet Union refused support.

	\item \textbf{NATO} $-$ An acronym for North Atlantic Treaty Organization. It was founded in 1949. It was intended to Ally countries so they could defend against a possible Soviet enemy.

    \item \textbf{Warsaw Pact} $-$ The Warsaw Pact, commonly shortened to WTO, was a (\emph{late}) response to NATO. It was founded in 1955. It contained the satellite states and the Soviet Union itself. It was signed into action in Warsaw, Poland (\emph{thus the name, Warsaw}).
    

    \item \textbf{Korean War} $-$ This was the first proxy war during the Cold War. The Soviets supplied the communist North Korea, while the UN (mainly the United States) supplied the South Koreans. Stalin intended this to be a test of American strength, capability, and resolve by instigating the perpetuation of American direct involvement. Soviet support of the Korean war effort ended shortly after Stalin's death, thus ending the war were it began, the \nth{38} parallel.

	\item \textbf{Christian Democrats} $-$ A progressive group of Catholics that became influential following the end of the Second World War.

	\item \textbf{Charles de Gaulle} $-$ He was the main French General during World War II. He later became the leader of the French Republic.

	\item \textbf{Labour Party (England)} $-$ This is generally known to be the opposition to the conservative party. The Labour Party is known to lean towards democratic socialism. They greatly support trade unions.

	\item \textbf{Keynesian Economics} $-$ Economic theories proposed by John Maynard Keynes. These theories revolve around the shot run and recessions, postulating that aggregate demand influences economics greatly during recessions.

    \item \textbf{Common Market} $-$ A designated geographical region with relatively free (\emph{free as in freedom}) trade regulations between most non-Soviet European nations; also known as the European Economic Community, the EEC was declared into effect in 1958 and became a commissioned legislative parliament accounting for the independent organization of trade between France, Germany, Greece, Italy, Netherlands, Portugal, Spain, and the constituents of the United Kingdom. 

    \item \textbf{Decolonization} $-$ A period officially demarcating the end of imperialistic domination by European \emph{pro}-\emph{western} superpowers of third world\footnote{alignment with neither the United States nor the Soviet Union.} countries such as Angola, Mozambique, and Vietnam.
      
    \item \textbf{Neocolonialism} $-$ A period following the decolonization of third world countries in which first and second world satellites established dominate roles over militaristic, economic, and social practices of the aforementioned third world countries in order to establish an allegiance of strongholds. Examples of this include the U.S. intervention in Vietnam, the Cuban intervention in Angola, and the Soviet intervention in Nicaragua.

    \item \textbf{Josip Broz Tito} $-$ A Yugoslavian revolutionary and communist sympathizer who successfully maintained neutrality of his nation from the NATO and WTO satellites. His reign marked a time of generally considered prosperity for all ethnicities of Yugoslavs, however the political instability after his death demarcate the heightened racial and religious turmoil that would evolve into the Balkan conflict of the 1990s.

    \item \textbf{Nikita Khruschev} $-$ A Ukrainian born Soviet diplomat who assumed power after his minimalist coup against Georgy Malenkov. Khruschev executed many changes such as the repeated national acts of amnesty, removal of architecture abundance, and restructuring of civilian housing arrangements. He befriended many high party officials during his tenure as chairman of Ukrainian party commissars during the Great Patriotic War and leveraged his connections to limit the growth of bonapartistic sentiment toward military leaders such as Zhukov and Voroshilov. He also oversaw the restructuring of the National Commissariat of Internal Affairs into the compartmentalized Committee of State Security which ousted Stalinist loyalists such as Lavrentiy Beria. Khruschev also extended Soviet diplomacy across the globe and traveled more during his time as General Secretary of the party than did Stalin during this entire reign. 

    \item \textbf{De-Stalinization} $-$ The period of official governmental recognition of the systematic repression during the Stalinist regime under the auspices of Marxism-Leninism.

    \item \textbf{Dr. Zhivago} $-$ A Soviet banned novel, «Доктор Живаго» (``Doctor Zhivago''), published in Italy by Russian born author Boris Pasternak who would later receive a Nobel prize in literature. He began writing since the end of the Second World War and took over a decade to complete. The narrative is told from the point of view of a wealthy adult entrepreneur named Zhivago and outlines the immense loss of life during the Russian revolution following the events of the First World War.

    \item \textbf{Alexandr Solzhenitsyn} $-$ A Russian born Soviet historian/philosopher and writer who opposed the Marxist-Leninist regime of gulag concentration in the Soviet Union and would bring global attention to its existence by authoring the «Архипелаг Гулаг» (``\emph{The Gulag Archipelago}'').

    \item \textbf{Peaceful Coexistence} $-$ A Soviet proposed idea of Marxist revisionism (\emph{contradictory to the Marxist-Leninist belligerent manifestation of anti-capitalist foreign policy)} that both capitalist and socialist states could exist in peace.

    \item \textbf{Hungary 1956} $-$ An anti-communist uprising resulting in the Soviet army having to engage in violent countermeasures to curb the spread of dissidence and anti-communist sentiment of the Hungarian government's inadequacy to take care of its citizens. 

    \item \textbf{Leonid Brezhnev} $-$ A Soviet engineer turned diplomat and World War Two veteran who was decided by the central committee to assume the role of party General Secretary after Nikita Khruschev. His reign demarcated the domestic political and economical stability amid numerous foreign policy triumphs. His death, however, created a power vacuum and ideological struggle among party members, military service members, and intelligence officers which would result in numerous foreign policy defeats and domestic miscalculations that would effectively result in the end of the Marxist-Leninist regime in the Soviet Union.

    \item \textbf{Berlin Wall} $-$ A physical barricading obstacle constructed in Berlin under the guidance of Soviet authorities in order to the minimize the influence of western industries such as media and marketing. The construction of the wall was a fitting metaphor for Churchill's proclamation of an iron curtain.

    \item \textbf{Czechoslovakia 1968} $-$ An anti-communist uprising similar to the one in Hungary in which the Soviet army and WTO armies (\emph{Romania excluded}) engaged in violent countermeasures to curb the spread of dissidence and anti-communist sentiment of Czechoslovakia's government's inadequacy to take care of its citizens.

    \item \textbf{Alexander Dub\u cek} $-$ The first secretary of the Communist Party of Czechoslovakia who proclaimed that ``\emph{socialism with a human face}'' would triumph however the worsening economic situation in Czechoslovakia would put pressure on Dub\u cek to strengthen his relationship with the Soviet Union. The instability of his regime would evolve into rioting instigating protests and would coerce the Soviet armed forces to take part in the interest of tranquility. His political career would effectively become less \emph{westernized} since the `68 uprising and he would since avoid military intervention so as to avoid ethnic instigations between Czech and Slovak people.

    \item \textbf{Brezhnev Doctrine} $-$ A Brezhnev era Soviet foreign policy that justified Soviet intervention in any eastern bloc satellite as a proactive measure in preserving the Marxist-Leninist ideology.

    \item \textbf{Silent Generation} $-$ The generation following the Greatest Generation and preceding the Baby Boomers.

    \item \textbf{Beat Generation} $-$ An American sub-culture during the 1950s post war reconstruction period that embraced sexual liberation (\emph{and psychedelic drugs like LSD}) and essentially rejected the materialism associated with socio-economic affluence. 

    \item \textbf{D\'etente} $-$ French for relaxation, a political situation characterized by a period of deescalating tensions such the period of foreign policy between the United States and the Soviet Union; a mutual coexistence promoted by Richard Nixon and Leonid Brezhnev.

    \item \textbf{Willy Brandt} $-$ A German politician involved with the Social Democratic Party (\emph{post Nazification}) who held the office of Chancellor (\emph{West Germany}) after his tenure as mayor of Berlin during the erection of the Berlin Wall. The name Brandt was merely a pseudonym for Herbert Frahm, which stuck following his successful evasion of the Nazi regime. Brandt favored intercourse with west and maintained connections among western politicians, diplomats, and intelligence officers and would even act as a western agent in Bundestag.

    \item \textbf{Helsinki Agreement (1975)} $-$ The Helsinki Agreement, signed during the D\'etente period, promoted peace across Europe. It was signed by the United States, the USSR, and 33 other states in both, NATO and WTO. First of all, it recognized borders of countries post-World War II (Meaning the USSR got control of Latvia, Lithuania, and Estonia). It also guaranteed civil rights to citizens in each country that signed the agreement. 

    \item \textbf{Margaret Thatcher} $-$ An English born Chemist turned politician proclaimed by a Soviet journalist to be an ``\emph{Iron Lady}''. Thatcher served as Prime Minister of the United Kingdom during the 1980s and was elected into office amid an ongoing recession and a general period of discontent and even survived a assassination attempt by the IRA. Although viewed internationally under the scrutiny of controversy she is, in England, viewed favorably as a three time head of state.    

    \item \textbf{Helmut Kohl} $-$ A German politician who served as Chancellor of Germany during the period demarcating the reunification of Germany following the tear down of the Berlin Wall. His time in office is viewed as a cornerstone synonymous with the modernization of Germany industry.

    \item \textbf{Simone de Beauvoir} $-$ A French born essayist and feminist philosopher involved with the theory of feminist existentialism and existential phenomenology. Her works gained her world fame and international recognition within the Parisian feminist movement, however her critics, of which there are many, accused her of being a western Marxist sympathizer.

    \item \textbf{Betty Friedan} $-$ An American born feminist writer and activist concerned with the liberal feminist attitudes toward abortion, pornographic compenstaion, lesbianism, and equal rights. She founded many feminist centered organization as well as authored ``\emph{The Feminine Mystique}'' and sparked the 1960s movement known as second-wave feminism. Her rhetoric influenced changed the behavior of many women over the course of the past few decades.

    \item \textbf{NOW} $-$ The National Organization of Women founded by Betty Friedan, among others, at the National Conference of Commissions on the Status of Women in 1966. The NOW mission is to promote the equality of rights under the law and encourage activism and the correct rhetoric to do so. The NOW is, essentially, a NAACP type organization for women. 

    \item \textbf{OPEC} $-$ The Organization of the Petroleum Exporting Countries, the mission of which is ``[to] coordinate and unify the petroleum policies of its member countries and ensure the stabilization of oil markets, in order to secure an efficient, economic and regular supply of petroleum to consumers, a steady income to producers, and a fair return on capital for those investing in the petroleum industry''. Established in Iraq in 1960 by, initially, Iran, Iraq, Kuwait, Saudi Arabia, and Venezuela and now has over twice as many origin members. 

    \item \textbf{Misery Index} $-$ An economic metric established to indicate the quality of life of the average citizen with respect to determinants such as inflation, unemployment, and social domestic considerations.

\item \begin{enumerate}[label=\alph*.]

    \item The Habsburg-Valois War and the Peace of \underline{Augsburg} (1555)
    \item The Thirty Years War and the Peace of \underline{Westphalia} (1648)
    \item The War of Spanish Succession and the Peace of \underline{Utrecht} (1715)
    \item The War of Austrian Succesion and the Peace of \underline{Aachen} (1748)
    \item The Seven Years War and the Peace of \underline{Paris} (1763)
    \item The Napoleonic Wars and the Peace of \underline{Paris} (1815)


\end{enumerate}

    \item The essential question that was ignored was: what about the 'satelite' states? Although Churchill and Roosevelt both knew about Stalin's wants, they did not want to provoke another war. Because of this, this question was left alone.

    \item At the Potsdam Conference, it was clear that the west did not intend to work together with Stalin. Because of this, Stalin adopted an 'iron' foreign policy. As a result, the west saw him as an enemy (which was created by them), and thus, the Cold War began.

    \item Following World War II, all of contiguous Europe's infrastructure had been destroyed. As such, America wanted to provide aid, and, because of this, the Marshall Plan was created. It offered support to all countries involved in the Second World War (Including the Soviet Union). The Truman Doctrine was created because of a theory titled the 'Domino Effect,' which stated that if one country falls to communism, others would begin to fall at an increasing rate. The Truman Doctrine would ultimately lead to the political differences that created the First, Second, and Third worlds.

    \item The authors of the book are claiming that the late opposition to Stalin's post-World War territorial claims significantly increased the tension, and possibly directly caused, the Cold War.

    \item World War II led to the creation of many useful machines and even the availability of air travel. It led to the study of atomic theory.

    \item Politically, the two groups to emerge were democratically elected leaders vs. dictators, or republicanism vs. communism, in this case. Economically, the fight was capitalism vs socialism. Communists wanted a global, single country (globalism), whereas the capitalist countries aided other countries to stimulate economic growth following the war.

    \item Following the Second World War, instead of isolation, the U.S. heavily influenced European affairs. Although this mostly took place in Germany, it did influence surrounding areas too.

    \item Europe rebuilt economies quickly thanks to two factors: the Marshall plan, and later, the Common Market. The Marshall Plan aided all countries by giving all supplies necessary to recover. The Common Market allowed the economies to grow and develop more robustly.

    \item The economic was much more successful. The Marshall Plan and Common Market are examples of the successes.

    \item The Common Market is one step taken towards economic unity. It was quite successful in unifying countries through trade.

    \item No, but radical Nationalist ideas were. The European countries needed to appeal to nationalism to be able to withstand communist influence. Charles de Gaulle was a French General-turned-Politican following the Second World War. He wanted to create a French Republic.

    \item Because a major part of the war was fought over Africa and other major colonies, people began to protesr imperialism. This resulted in decolonization.

    \item In India, nationalist movements would be led by Mahatma Gandhi. They would take the form of peaceful protest, with no aggression. In China, the Nationalists would fight the Communists for control of the government.

    \item \begin{enumerate}[label=\alph*.]

    \item Sri Lanka had a peacful protest movement, much alike India. They wanted to achieve independence from British Ceylon. The Burmese revolted against the Japanese towards the end of World War II.

    \item The Indonesians fought the Netherlands for independence, which they gained in 1949.

    \item The Indochinese (or better known Vietnam) declared independence hours following the surrender.

    \end{enumerate}

    \item A major political problem in the Middle East was the development of the Jewish nation-State, Israel. Palestinian Muslims, to this day, fight with the Israeli Jewish.

    \item The African colonies, although now liberated, began to grow better ties with their former 'governors.' This is because these African colonies were at risk for being taken under communism. Examples include Angola and Mozambique.

    \item Some did. some didn't. This was like any other political movement or declaration.

    \item The status quo was changed because of the growing poulation, growing industries, and a new feeling of self-worth. The fear of communism spreading in the US was a big driverin such changes. This took place in the 50s and 60s.

    \item One good thing that came from the war was that African Americans were included in the armed forces during the war. Also, women were more accepted in the workplace, as they supplied the front by working in factories. Also, the Helsinki Agreements guaranteed civil rights to all people in the countries that signed the agreement.

    \item Post-war, Stalin wanted to work with western countries, however, they didn't want to work with him. Russian nationalists were dissapointed because Stalin was not Russian, however he was controlling them. Stalin was the most firm ruler of the Soviet Union.

    \item Khrushchev's Twentieth Party Congress was attempted to be censored by the high party officials. Khrushchev, however, went out and said his speech anyways. The speech denounced Stalin directly, and, as such, showed that the communist system was flawed.

    \item The results of deStalinization effected Soviet foreign policy throughout the end of the 1950s by causing an ideological shift acknowledged formally as Marxist revisionism. This ideological shift contributed to the degrading diplomatic relationship between the Soviet Union and the Chinese Communist Republic resulting in the eventual Sino-Soviet schism of the 1960s.

    \item Not only did Khurshchev go against the Party, but he also handled himself poorly in situations like the Cuban Missle Crisis. Because he disgraced the Soviet Union in such ways, the Party decided he was not fit to rule.

    \item Under Brezhnev, the Soviet Union had an era of economic stability. Although there were relative food shortages, they were not nearly as bad as the shortages under Stalin. Economic stability, however, can also be interpreted as a negative because there was no economic growth.

    \item The Prague Spring was caused by the election of Alexander Dub\u cek. He was a liberal reformer, and, as such, wanted to modify the censorship that the people lived under. Because this threatened the Soviet control over Czechoslovakia, a conflict arose. Although limited freedoms would be passed, they would be no where near the scale that Dub\u cek wanted. The west wanted it to occur to show the oppression people lived under in Soviet territory.

    \item A Brezhnev era Soviet foreign policy that justified Soviet intervention in any eastern bloc satellite as a proactive measure in preserving the Marxist-Leninist ideology.

    \item "Big Science" came into existence following the Manhattan Project. This was because people began to become interested in the sciences. NASA and engineering universities such as MIT became world famous agencies and institutions, respectively. The Soviet Union had RosKosmos (a cosmology program). The purpose of Big Science was to research the world around us.

    \item Einstein recieved life tenure at Princeton University. Many future scientists and engineers would look up to people like Einstein and follow in their steps.
    
    \item A defining characteristic was individual freedom. This would transition, after the World Wars, into the 'American Dream' and material freedom. This change is being reversed because of the modern liberal movement.

    \item With the availability of all things necessary for life, people were able to set goals in other areas, such as starting a business. As such, people could climb the 'class' ladder because in America, it was free and mobile.

    \item The Baby Boomers were much more self-centered and individual. They could make a good amount of money with only a high school diploma, and saw family as a broad topic, due to rising divorce levels.

    \item The Vietnam War awareness escalated quickly among civilians because it was the first broadcasted war. Student radicalism began because of the draft targeting students. 

    \item The youth were infatuated with non-materialistic ideologies. Because of this, they revolted in France in May of 1968. They wanted  to stand up to the dullness of life in de Gaulle's France. It was predictable that the election would see that the liberal leader would become the head of the government.

    \item \textbf{Gdansk Agreement of 1980} $-$ Lech Walesa, leader of the Polish solidarity movement, signed this agreement, which gave workers a five-day work week, pay increases, the right to strike, and the right to form trade unions.

    \item \textbf{Single European Act of 1986} $-$ This act saw that the tariffs and trade barriers between European countries were abolished. The act aimed to unify trade. 

    \item \textbf{Maastricht Treaty of 1990} $-$ Among many other things, the Maastricht Treaty established the base of the EU.

    \item \textbf{Paris Accord of 1990} $-$ America signed this treaty to withdraw troops from Vietnam, however, the North Vietnamese took over th South in 1975 anyways.

    \item \textbf{"Polish Miracle" of 1980} $-$ This occurred when the economic crisis turned into a spiritual one. Pope John Paul II called attention to workers rights. Lech Walesa created the Solidarity as a result of this.

    \item \textbf{Solidarity} $-$ Polish trade union created in 1980 to protest working conditions. 

    \item \textbf{Perestroika} $-$ It was Gorbachev's plan for economic restructuring.

    \item \textbf{Glasnost} $-$ It was a policy of honest politics from the Soviet Union.

    \item \textbf{the Euro} $-$ A currency that, to this day, is used in all European countries.

    \item \textbf{Mikhail Gorbachev} $-$ The last Soviet politican. He tried to bring peace in the cold war, however, it led to the end of the Soviet Union. 

    \item \textbf{Boris Yeltsin} $-$ First leader of Russia following the collapse of the Soviet Union. He drafted a new constitution, and drew inspiration from France.

    \item \textbf{Lech Walesa} $-$ Leader of the Solidarity movement in Poland. He worked for the workers, in order to make life more democratic in Poland. 

\end{enumerate}
\end{flushleft}
\end{document}

