\documentclass[a4paper]{article} 
\usepackage{tcolorbox}
\tcbuselibrary{skins}

\title{
\vspace{-3em}
\begin{tcolorbox}[colframe=white,opacityback=0]
\begin{tcolorbox}
\Huge\sffamily Vocabulary and Definitions
\end{tcolorbox}
\end{tcolorbox}
\vspace{-3em}
}

\date{}

\usepackage{background}
\SetBgScale{1}
\SetBgAngle{0}
\SetBgColor{grey}
\SetBgContents{\rule[0em]{4pt}{\textheight}}
\SetBgHshift{-2.3cm}
\SetBgVshift{0cm}

\usepackage{lipsum}% just to generate filler text for the example
\usepackage[margin=2cm]{geometry}

\usepackage{tikz}
\usepackage{tikzpagenodes}

\parindent=0pt

\usepackage{xparse}
\DeclareDocumentCommand\topic{ m m g g g g g}
{
\begin{tcolorbox}[sidebyside,sidebyside align=top,opacityframe=0,opacityback=0,opacitybacktitle=0, opacitytext=1,lefthand width=.3\textwidth]
\begin{tcolorbox}[colback=red!05,colframe=red!25,sidebyside align=top,width=\textwidth,before skip=0pt]
#1\end{tcolorbox}%
\tcblower
\begin{tcolorbox}[colback=blue!05,colframe=blue!10,width=\textwidth,before skip=0pt]
#2
\end{tcolorbox}
\IfNoValueF {#3}{
\begin{tcolorbox}[colback=blue!05,colframe=blue!10,width=\textwidth]
#3
\end{tcolorbox}
}
\IfNoValueF {#4}{
\begin{tcolorbox}[colback=blue!05,colframe=blue!10,width=\textwidth]
#4
\end{tcolorbox}
}
\IfNoValueF {#5}{
\begin{tcolorbox}[colback=blue!05,colframe=blue!10,width=\textwidth]
#5
\end{tcolorbox}
}
\IfNoValueF {#6}{
\begin{tcolorbox}[colback=blue!05,colframe=blue!10,width=\textwidth]
#6
\end{tcolorbox}
}
\IfNoValueF {#7}{
\begin{tcolorbox}[colback=blue!05,colframe=blue!10,width=\textwidth]
#7
\end{tcolorbox}
}
\end{tcolorbox}
}

\def\summary#1{
\begin{tikzpicture}[overlay,remember picture,inner sep=0pt, outer sep=0pt]
\node[anchor=south,yshift=-1ex] at (current page text area.south) {% 
\begin{minipage}{\textwidth}%%%%
\begin{tcolorbox}[colframe=white,opacityback=0]
\begin{tcolorbox}[enhanced,colframe=black,fonttitle=\large\bfseries\sffamily,sidebyside=true, nobeforeafter,before=\vfil,after=\vfil,colupper=black,sidebyside align=top, lefthand width=.95\textwidth,opacitybacktitle=1, opacitytext=1,
segmentation style={black!55,solid,opacity=0,line width=3pt},
title=Summary
]
#1
\end{tcolorbox}
\end{tcolorbox}
\end{minipage}
};
\end{tikzpicture}
}

\usepackage{graphicx}
\usepackage{physics}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{mathdots}
\usepackage{yhmath}
\usepackage{cancel}
\usepackage{color}
\usepackage{siunitx}
\usepackage{array}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{hyperref}
\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,      
urlcolor=blue,
citecolor=blue,
}
\urlstyle{same}
\usetikzlibrary{fadings}
\usetikzlibrary{patterns}
\usetikzlibrary{shadows.blur}
\usetikzlibrary{shapes}

\begin{document} 
\maketitle

\topic{Exigence}{The need or demand. Why is \underline{NOW} the time \& place for a message}%

\topic{Rhetoric}{The ability to discern the available means of persuasion in any given situation.}%

\topic{Visual Rhetoric}{``Writing with images'' Ex. documentaries, illustrations, advertisements, cartoons, etc.}%

\topic{Audience}{A group to whom a work is meant to be presented to. Must establish what the viewer's values or morals are in order to have an effective message}%

\topic{Text}{Products meant to be read}%

\topic{Context}{Parts of discourse that surround a word or passage}%

\topic{Rhetorical Triangle}{A way to conceptualize the relationship between elements of a text}%

\summary{\centering\include{Figures/RhetTriangle}}

\newpage

\topic{Occasion}{Specific circumstances surrounding the creation of a text}%

\topic{Purpose}{The goal an author intends to achieve}%

\topic{Speaker}{The author of the text}%

\topic{Persona}{The difference between the speaker on and off stage}%

\topic{Subject}{The topic of the text}%

\topic{Ethos}{Greek word for character. Expertise, knowledge, sincerity. Conveys shared values}%

\topic{Pathos}{Emotions, desires, hopes, fears, prejudices. Rests with connotations}%

\topic{Logos}{Clear rational ideas, backed with statistics, examples, or details. Logic}%

\topic{\textit{The King's Speech}}{Answer the questions}%

\topic{Question 1 $-$ How do you think King George VI felt during this speech?}{First and foremost, King George VI most likely feared for himself and his people. In addition to this, he probably felt powerful, as all of his citizens were listening to him at once. Also, he probably feels anxious and concerned about going into the war.}%

\topic{Question 2 $-$ What is the emotion behind this speech?}{Sorrow, courage, patriotic, powerful.}%

\topic{SPACECAT}{\begin{tabular}{r|l} S & peaker \\ P & urpose \\ A & udience \\ C & ontext \\ E & xigence \\ C & hoices \\ A & ppeals  \\ T & one  \\ \end{tabular}}%

    \topic{When thinking of the speaker\dots}{What are their beliefs and values? Do we trust them? Why? What do we know and not know about them? Is there meaning behind who wrote or said it?}%

    \topic{When thinking of the purpose\dots}{What is the speaker hoping to accomplish? What reaction are they trying to elicit, and how do they want us to behave? Think of the purpose as an infinitive: to + verb.}%

    \topic{When thinking of the audience\dots}{What did the speaker assume about their audience? How does that impact what they say and how they say it?}%

    \topic{When thinking of the context\dots}{What was going on in the world when this text was produced?}%

    \topic{When thinking of the exigence\dots}{What was the spark or catalyst that moved the speaker to act?}%

    \topic{When thinking of the choices\dots}{This is a category of all the little moves authors make to enrich their writing. Why does the writer make each choice?}%

    \topic{When thinking of the appeals\dots}{Appeals to the ethics or credibility, emotion, or logic or reason.}%

    \topic{When thinking of the tone\dots}{What is the speaker's attitude at different places throughout the text? How can you tell this is their attitude? Where does the tone shift in the piece?}%

    \topic{Examples: Spread vs Smear, Weep vs Cry vs Sob}{Connotation $-$ The certain feeling behind a word or phrase}%

    \topic{Diction}{A speaker's choice of words.}%

    \topic{Syntax}{How the words are arranged.}%

    \topic{Tone}{The speaker's attitude toward the subject as revealed by his or her choice of language.}%

    \topic{Mood}{The feeling created by the work.}%

    \topic{Metaphor}{A word or phrase that represents something other than the top meaning.}%

    \topic{Simile}{When two things are compared, usually using the phrases: \textit{like}, or \textit{as\dots as}.}%

    \topic{Personification}{When an inanimate object is given human attributes and characteristics.}%

    \topic{Hyperbole}{An obvious exaggeration.}%

    \topic{Parallelism}{Use of similar or identical syntaxes in different clauses or phrases.}%

    \topic{Juxtaposition}{When two things are placed side by side, usually to compare.}%

    \topic{Antithesis}{Synonymous with counterclaim.}%

    \topic{Compound Complex}{A sentence that uses the structure of both, a compound and a complex sentence.}%

    \topic{Periodic}{Something recurring in intervals.}%

    \topic{Cumulative}{Something that increases in size.}%

    \topic{Imperative}{When something is conveyed as necessary or urgent.}%

    \topic{Imagery}{The use of mental pictures or images.}%

    \topic{Oxymoron}{When two contradictory items are placed together.}%
 
    \topic{Horative Sentence}{Expressions used by the speaker to encourage or discourage an action.}%

    \topic{In visual arguments (like advertisements) \dots \textbf{background}}{Something that may be used to give a different impression of the object in the foreground.}%

    \topic{In visual arguments (like advertisements) \dots \textbf{focus}}{Focus purposely makes the consumer see what the advertiser wants, like only the product itself.}

    \topic{In visual arguments (like advertisements) \dots \textbf{line}}{A line (such as a line on the horizon created by a sunset) may be used in visual advertisements to calm the viewer.}

    \topic{In visual arguments (like advertisements) \dots \textbf{shape}}{Softer edges in visual advertisements give certain products gentler, more organic looks.}

    \topic{In visual arguments (like advertisements) \dots \textbf{framing}}{Framing an object in the center of a shot strategically makes the object appear better, especially if there is a calming (and, therefore, convincing) background.}

    \topic{In visual arguments (like advertisements) \dots \textbf{foreground}}{The opposite of background. Something in the foreground is right upfront, to be purposely seen by a viewer.}


    \topic{Types of speech\dots \textbf{Epideictic}}{Bestowing praise or blame on a person or phenomenon}

    \topic{Types of speech\dots \textbf{Juridicial}}{Defending or accusing someone}

    \topic{Types of speech\dots \textbf{Deliberative}}{Giving advice for the future by arguing for or against a particular cause}

    \topic{A Rhetorical Analysis Thesis has four parts}{\begin{itemize} \item Name of the author, genre, title WITH a rhetorically accurate verb (asserts, argues, claims) and a THAT clause containing the major assertion (thesis statement) of the work. \item An explanation of how the author develops and/or supports the thesis, usually in chronological order. \item A statement of the author's apparent purpose followed by an ``in order to'' phrase. \item A description of the intended audience and the relationship the author establishes with the audience. \item Ex. Billy Jo Thornbob, poet laureate, in his poem, ``My Beetle Jeetle'',  asserts that all children should own a pet because they make us more responsible and empathetic. He utilizes positively connotative language, a dogmatic tone that appeals to our logic, and both tactile and visual imagery in order to convince the audience $-$ parents of small children $-$ to heed his hypothesis, which will result in a more responsible and empathetic world population. \end{itemize}}

    \topic{Rank in order of importance (for Collegeboard)\dots Ideas, scholarly diction, scholarly syntax, organization}{\begin{tabular}{c|c} 1 & Ideas \\ 2 & Organization \\ 3 & Scholarly syntax \\ 4 & Scholarly diction \\  \end{tabular}}%

    \topic{How should you write your essay?}{Use a structure, not a formula. Formulas will make one sound robotic and lacking of character}%

    \topic{Three types of questions we will receive}{\begin{tabular}{c|c} 1 & Synthesis\footnote{A DBQ-style question, where one usually deals with current events, and must develop a position and support your thesis with the 6-8 provided sources.} \\ 2 & Rhetorical Analysis\footnote{First read a piece of rhetoric, then analyze the ways the writer achieves their purpose.} \\ 3 & Argument\footnote{Given a question, develop a stance and argue it.} \\ \end{tabular}}%

    \topic{Intro Paragraph format}{\begin{tabular}{c|c} Type & Length \\ \hline Hook & 1$-$2 \\ Setup & 3$-$5 \\ Thesis & 1$-$2 \\ \end{tabular}}%

    \topic{How to correctly use verb tenses in rhetorical analysis essays}{When you write about the context, use the past tense. When you write about the text itself and choices of the speaker, use present tense.}%

    \topic{Flow of body paragraphs}{\begin{enumerate} \item Meaningful transition (1 sentence)  \item Topic sentence (1 sentence)  \item First piece of evidence (1 sentence)  \item Analysis of evidence (2$-$4 sentences)  \item Second piece of evidence (1 sentence)  \item Analysis of second evidence (2$-$4 sentences)  \item Synthesis (1$-$2 sentences)  \end{enumerate}}%

    \topic{Conclusions aren't in the rubric, so don't spend lots of time on them}{\begin{enumerate} \item Reinforce the context and exigence of the speech and why it was so important for these choices to be made \item Describe the effects of the speech (if you know anything about the speech's effects) \item Provide a general summation of the choices made and why they were necessary \item Build on a metaphor that was started in the intro  \end{enumerate}}%

    \topic{Anaphora}{The use of a word referring to or replacing a word used earlier in a sentence, to avoid repetition, such as do in I like it and so do they.}%

    \topic{Penultimate}{Second to last, next to ultimate}%

    \topic{Argument}{A persuasive discourse, a coherent and considered movement from a claim to a conclusion}%

    \topic{Rogerian Argument}{Having a full understanding of the other side is essential to responding because knowing the other side will not alienate or antagonize the other side}%

    \topic{Facts}{Claiming something is true or untrue. Use facts to verify claim. Draws logical inferences.}%

    \topic{Values}{May be personal judgements based on taste, values, morals. Laws and public policy originate from propositions of value.}%

  \topic{Closed Thesis}{The statement of the main idea of the argument that also previews the major point of the argument. It's closed because it limits the number of points that will be made.\\ \textit{Ex. Spectacular lights, expanded buffets, and world class shows make Las Vegas a true vacation destination.}}%

  \topic{Open Thesis}{Does not list main points. The type of thesis is intended for longer topics with many points. Tou can do this on a timed essay, but a novice writer runs the risk of veering off into the weeds.\\ \textit{Ex. Las Vegas is an adult playground with world-wide appeal.}}%

  \topic{Logical Fallacies}{The mistaken use of logos (logic).}%

  \topic{Red Herring}{Skips to another irrelevant topic.}%

  \topic{Ad Hominem}{Questioning the character of the speaker instead of the topic at hand.}%

  \begin{flushleft}

    \Large Fallacies of Accuracy:

  \end{flushleft}

  \topic{Faulty Analogy}{Comparing two things that are not comparables (e.g. Tiger Woods advertising a Rolex)}%

  \topic{Straw Man}{A straw man fallacy occurs when someone takes another person's argument of point, distorts it or exaggerates it in some kind of extreme way, and then attacks the extreme distortion as if that is really the claim the first person was making.\\ Ex: Person 2: We should have one non-Christmas song in the holiday shows. \\ Person 2: You won't be happy and all Christmas songs are banned in stores and on the radio. This is war on Christmas!}%

  \topic{Slippery Slope}{A slippery slope argument (SSA), in logic, critical thinking, political rhetoric, and case law, is often viewed as a logical fallacy in which a party asserts that a relatively small first step leads to a chain of related events culminating in some significant (usually negative) effect.}%

  \topic{Either/Or, False Dilemma, or False Dichotomy}{Two extreme choices are presented as the only option. \\ Ex: Either we all commit to electric cars and minimize our travels to no more than 10 miles or our children will not have a planet in 10 years. }%

  \topic{Equivocation}{Misleading the audience by using a word with a double or ambiguous meaning. \\ Ex: Noisy children are a real headache. Two aspirin will make a headache go away. Therefore, the aspirin will make noisy children go away.}%

  \begin{flushleft}

    \Large Fallacies of Insufficiency:

  \end{flushleft}

  \topic{Hasty Generalization}{A conclusion made about all or many. Not enough evidence to support a particular claim.}%

  \topic{Circular Reasoning}{Repeat the claim to provide evidence. \\ Ex: You must obey the law, because it's illegal to break the law.}%

  \topic{First Hand Evidence}{Is something you know. You have insider knowledge, observations, experiences. It provides some ethical aspects, but is NOT generally a universal experience.}%

  \topic{Second Hand Evidence}{Evidence accessed through research, reading and investigation. This is an appeal to logic.}%

  \topic{Historical Information}{Facts a writer knows from research. This is a strong strategy because it shows the writer took the time to research the matter. Considered the cause and effect.}%

  \topic{Post hoc Ergo Propter Hoc}{After this, therefore resulting from it: used to indicate that a casual relationship has erroneously been assumed from a merely sequential one.}
    
%\topic{Here's another question to begin the new page.}{\lipsum[3]}%
%{\lipsum[4]}%
%{\lipsum[5]}%

%\summary{And another summary that will float to the bottom of the next page.}

\end{document}
