\documentclass[12pt]{article}
\usepackage[letterpaper]{geometry}
\usepackage{amsmath, amsthm, amssymb, amsfonts}
\usepackage{graphicx}
\usepackage{titling}
\usepackage{hyperref}
\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%
}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
} 
\urlstyle{same}
\title{The Living Earth\\\underline{What Does \textbf{\textit{DNA}} Actually Look Like?!}}
\subtitle{Laboratory Assignment \#2}
\author{Michael Brodskiy}
\begin{document}
\maketitle
\begin{center} \textbf{\textsc{Post$-$Lab Conclusion}} \end{center} 
\newpage
{\setlength{\parindent}{0cm} \textbf{Objective}}
\paragraph{} The purpose of this laboratory experiment is to examine the resemblance of DNA molecules under the scrutiny of the naked eye.
    The specimens from which the DNA was extracted included strawberries and human cheek cells.
    Comparisons between the two yielded interesting results as witnessed foremost by James Watson and Francis Crick.
\begin{center}\end{center} 
{\setlength{\parindent}{0cm} \textbf{Outline}}
\paragraph{} The conducted procedure for this laboratory experiment started by pouring 50[$ml$] of a pre-mixed solution provided by the instructor. 
    Then 2 strawberries were placed into a ziploc bag and pulverized into a semi-liquid state. 
    After that, the mashed strawberries, along with the pre-mixed solution as well as isopropyl alcohol were poured into a test tube.
    A few seconds later, A white, semi-translucent liquid appeared at the top of the test tube: the DNA of the strawberries.
    The DNA was then placed on a piece of paper and carefully examined.  
\begin{center}\end{center} 
{\setlength{\parindent}{0cm} \textbf{Result}}
\paragraph{} The observable conclusion of this laboratory experiment remained non-discrepant for both DNA extractions. 
    Both the strawberry and the cheek cells looked like a white, somewhat clear, semi-liquid.
    The white lines among the interior of the extracted semi-liquids did look like loose DNA.
        \\
\end{document}
