%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Written By Michael Brodskiy
% Class: AP Environmental Science
% Instructor: Mrs. Stansbury
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt]{article} 
\usepackage{alphalph}
\usepackage[utf8]{inputenc}
\usepackage[russian,english]{babel}
\usepackage{titling}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{physics}
\usepackage{tikz}
\usepackage{mathdots}
\usepackage{yhmath}
\usepackage{cancel}
\usepackage{color}
\usepackage{siunitx}
\usepackage{array}
\usepackage{multirow}
\usepackage{gensymb}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{soul}
\usetikzlibrary{fadings}
\usetikzlibrary{patterns}
\usetikzlibrary{shadows.blur}
\usetikzlibrary{shapes}
\usepackage[super]{nth}
\usepackage{expl3}
\usepackage[version=4]{mhchem}
\usepackage{hpstatement}
\usepackage{rsphrase}
\usepackage{everysel}
\usepackage{ragged2e}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{cancel}
\geometry{top=1.0in,bottom=1.0in,left=1.0in,right=1.0in}
\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%

}
\usepackage{hyperref}
\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,      
urlcolor=blue,
citecolor=blue,
}

\urlstyle{same}


\title{Sewage Pollution Analysis}
\date{\today $-$ Period 1}
\author{Michael Brodskiy\\ \small Instructor: Mrs. Stansbury}

% Mathematical Operations:

% Sum: $$\sum_{n=a}^{b} f(x) $$
% Integral: $$\int_{lower}^{upper} f(x) dx$$
% Limit: $$\lim_{x\to\infty} f(x)$$

\begin{document}

\maketitle

\begin{enumerate}

  \item What is the concentration of nitrogen in the coastal area closest to where you live?

    \begin{itemize}

      \item Around 10,000,000 grams of nitrogen in the bay, and 100,000 grams in the coastal areas

    \end{itemize}

  \item Can you find any places that receive 100,000,000 grams of nitrogen per year? What about 1,000,000,000 grams?

    \begin{itemize}

      \item There are a good amount of  areas that receive 100,000,000 grams or more, usually next to major coastal cities; however, few areas with 1 billion or more grams exist, mostly on the coastal areas of China

    \end{itemize}

  \item What do you notice about the places that light up?

    \begin{itemize}

      \item The brightest areas generally correspond to the most population-dense cities, such as Moscow, Los Angeles, or northern Germany

    \end{itemize}

  \item Some areas are hotspots for coral wastewater impact. These have lots of red dots clustered together. Where are these areas? What do they have in common?

    \begin{itemize}

      \item The most red dots occur in coastal locations next to the most population-dense countries, like Brazil, India, and areas in southeast Asia

    \end{itemize}

  \item Where are corals less likely to experience risks from nitrogen?

    \begin{itemize}

      \item It seems like the least affected corals occur in open water, away from any smaller water corridors, like the Suez Canal, or island-dense area, like the Caribbean

    \end{itemize}

  \item What are hotspots for seagrass wastewater impact?

    \begin{itemize}

      \item Like corals, it seems like seagrass beds are most affected in coastal areas next to dense cities, like New York, southeastern China, and southern France/eastern Spain

    \end{itemize}

  \item Where is seagrass less likely to experience risks from nitrogen? 

    \begin{itemize}

      \item Seagrass beds seem to be least affected in island areas, like near New Zealand, Australia, or the UK
        
    \end{itemize}

\end{enumerate}

\end{document}

