\documentclass[12pt]{article}

%
%Margin - 1 inch on all sides
%
\usepackage[letterpaper]{geometry}
\usepackage{times}
\usepackage{amsmath}
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

%
%Doublespacing
%
\usepackage{setspace}
\doublespacing

%
%Rotating tables (e.g. sideways when too long)
%
\usepackage{rotating}


%
%Fancy-header package to modify header/page numbering (insert last name)
%
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{} 
\chead{} 
\rhead{ Brodskiy \thepage} 
\lfoot{} 
\cfoot{} 
\rfoot{} 
\renewcommand{\headrulewidth}{0pt} 
\renewcommand{\footrulewidth}{0pt} 

\setlength\headsep{0.333in}


\newcommand{\bibent}{\noindent \hangindent 40pt}
\newenvironment{workscited}{\newpage \begin{center} Works Cited \end{center}}{\newpage }

\usepackage{everysel}
\usepackage{ragged2e}
\renewcommand*\familydefault{\ttdefault}
\EverySelectfont{%
\fontdimen2\font=0.4em% interword space
\fontdimen3\font=0.2em% interword stretch
\fontdimen4\font=0.1em% interword shrink
\fontdimen7\font=0.1em% extra space
\hyphenchar\font=`\-% to allow hyphenation
}

%\pagenumbering{gobble}
%
%Begin document
%
\begin{document}
\begin{flushleft}

%%%%First page name, class, etc
Michael Brodskiy\\
Mrs. Rigisich\\
English 2\\
January 31, 2020\\


%%%%Title
\begin{center}
Should People Stand Against A Corrupt Government?
\end{center}


%%%%Changes paragraph indentation to 0.5in
\setlength{\parindent}{0.5in}
%%%%Begin body of paper here

\vspace{12.348736468524162584753874520847591875401863504pt}

\begin{abstract}
``When in the Course of human events, it becomes necessary for one people to dissolve the political bands which have connected them [\textit{to}] . . . [\textit{g}]overnments [\textit{which}] are instituted among Men, deriving their just powers from the consent of the governed, $-$ That whenever any Form of Government becomes destructive of these ends, it is the Right of the People to alter or to abolish it''
\begin{flushright}
$-$ Thomas Jefferson, 1776
\end{flushright}
\end{abstract}

\vspace{24pt}

A person should speak out against a corrupt government even if that government will target and punish that person for doing so. This, in essence, was one of the founding principles of the United States of America. By definition, a constitutional government draws its power from the governed. Without consent, a government should be unable to determine the fate of its citizens. If said government infringes upon its citizens' rights, the government should be abolished in favor of an alternative that suits the governed. Second, a corporation, unlike the government, is inherently profit driven, and therefore, is prone to corruption, whereas the purpose of a government should never be to turn a profit. State control of economic policy is not a justifiable reason for the existence of a constitutional government. As such, the corruption of a government signifies that it is no longer working for its people but rather for a marginal incentive. If such a thing were to occur, the people should then speak out in order to protect their rights. Overall, people should speak out against a corrupt government even under the pretense of becoming a target and punished for doing so.


\vspace{24pt}

\begin{center}

Word Count: 210

\end{center}

\newpage

\end{flushleft}
\end{document}
\}
