
\documentclass[12pt]{article} 
\usepackage{alphalph}
\usepackage[utf8]{inputenc}
\usepackage[russian,english]{babel}
\usepackage{titling}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage[super]{nth}
\usepackage{everysel}
\usepackage{ragged2e}
\usepackage{geometry}
\usepackage{fancyhdr}
\geometry{top=1.0in,bottom=1.0in,left=1.0in,right=1.0in}
\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%

}

\usepackage{setspace}
\doublespacing

\usepackage{hyperref}
\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,      
urlcolor=blue,
citecolor=blue,
}

\urlstyle{same}
%\renewcommand*\familydefault{\ttdefault}
%\EverySelectfont{%
%\fontdimen2\font=0.4em% interword space
%\fontdimen3\font=0.2em% interword stretch
%\fontdimen4\font=0.1em% interword shrink
%\fontdimen7\font=0.1em% extra space
%\hyphenchar\font=`\-% to allow hyphenation
%}

\pagestyle{fancy}
\lhead{Michael Brodskiy}
\rhead{Page \thepage}
\chead{APUSH SAQ}
\cfoot{}

\begin{document}

\begin{enumerate}

  \item $-$ Version D

    \begin{enumerate}

      \item Within this letter, Benjamin Franklin describes the English making conquest of the American States. This is in reference to the beginning of the American Revolutionary war, which is said to have started during the Battle of Lexington and Concord, in 1775. As such, after over a year of tension, Benjamin Franklin is writing to the French count of Vergennes to request support in combat.

      \item The aforementioned event, the American Revolutionary War, marked a new era for the American colonies. After the war was a time period for the development of a new nation, the first time the British throne had been overthrown. This fledgling nation would (at first, poorly) survive and have to set up its own system of government if it wanted to become strong. As such, a big change which occurred as a result of the American revolutionary war was the creation of a new nation, independent from the British rule.

      \item Benjamin Franklin is writing to the foreign minister of France. As such, it is well known that the French, after some reluctance, aided the American nation in their fight to overcome the British. Therefore, it is clear that Franklin is addressing the foreign minister concerning assistance on the American front.

    \end{enumerate}

  \item $-$ Version D

    \begin{enumerate}

      \item The Articles of Confederation's most important historical development is that it defined the parameters with which a new nation was to rule. It was the first actual piece of governing legislation passed to form a new government, and, as such, it somewhat defined the American states, showing they were now separate from their previous British ruler.

      \item One big concern was the matter of taxation. Many critics believed that a unanimous vote for a tax was completely unreasonable. In addition to this, the colonial economy and militia was in shambles following their combat with the British. As a result, government funds were needed to pay the militia men, as well as to stimulate the economy.

      \item Most importantly, the Constitution allowed the federal government the right to tax $-$ though not without some difficulty $-$ even though it wasn't nearly as difficult as with the Articles of Confederation. As such, many people who believed the Articles of Confederation to be flawed agreed with passing the Constitution, as it allowed for easier federal taxation.

    \end{enumerate}

\end{enumerate}

\end{document}
