\documentclass[12pt]{article}

%
%Margin - 1 inch on all sides
%
\usepackage[letterpaper]{geometry}
\usepackage{times}
\usepackage{amsmath}
\usepackage{hyperref}
\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,      
urlcolor=blue,
citecolor=blue,
}

\urlstyle{same}
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

%
%Doublespacing
%
\usepackage{setspace}
\doublespacing

%
%Rotating tables (e.g. sideways when too long)
%
\usepackage{rotating}


%
%Fancy-header package to modify header/page numbering (insert last name)
%
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{} 
\chead{} 
\rhead{ Brodskiy \thepage} 
\lfoot{} 
\cfoot{} 
\rfoot{} 
\renewcommand{\headrulewidth}{0pt} 
\renewcommand{\footrulewidth}{0pt} 

\setlength\headsep{0.333in}


\newcommand{\bibent}{\noindent \hangindent 40pt}
\newenvironment{workscited}{\newpage \begin{center} Works Cited \end{center}}{\newpage }

\usepackage{everysel}
\usepackage{ragged2e}
%\renewcommand*\familydefault{\ttdefault}
%\EverySelectfont{%
%\fontdimen2\font=0.4em% interword space
%\fontdimen3\font=0.2em% interword stretch
%\fontdimen4\font=0.1em% interword shrink
%\fontdimen7\font=0.1em% extra space
%\hyphenchar\font=`\-% to allow hyphenation
%}

%\pagenumbering{gobble}
%
%Begin document
%
\begin{document}

%%%%First page name, class, etc
Michael Brodskiy\\
Mrs. Greer\\
AP Language and Composition\\
Summer Assignment\\


%%%%Title
\begin{center}
  Charles Krauthammer $-$ \href{https://www.washingtonpost.com/opinions/charles-krauthammer-the-enduring-miracle-of-the-american-constitution/2018/11/29/fb8879d2-f405-11e8-aeea-b85fd44449f5_story}{Article 1} Pr\'ecis
\end{center}


%%%%Changes paragraph indentation to 0.5in
\setlength{\parindent}{0.5in}
%%%%Begin body of paper here

\begin{justify}
\begin{enumerate}

  \item Charles Krauthammer, a political commentator, writes about the American Constitution and its lasting effects in his column titled, ``The Enduring Miracle of the American Constitution'' (November 29, 2018), excerpted from Krauthammer's book, ``The Point of it All.'' Krauthammer begins by bringing up a memory of a switch of power in Egypt, comparing the Egyptian attitudes towards their respective constitution to that of America; Krauthammer uses this as a segue into, what he refers to, as the three miracles of the American constitution. Krauthammer writes this (opinion) column in order to marvel at the lasting influence of the American constitution, and to convince the reader that such adherence and reverence to a document is extraordinary. As such, the author connects with the American public by commenting upon the astounding roots of the country known as the United States of America. 
\end{enumerate}
\newpage

\begin{center}
  Charles Krauthammer $-$ \href{https://www.washingtonpost.com/opinions/charles-krauthammer-the-authoritarian-temptation/2019/11/08/a55427f4-01a2-11ea-8bab-0fc209e065a8_story}{Article 2} Pr\'ecis
\end{center}
\begin{enumerate}
    \setcounter{enumi}{1}
  \item A political commentator by the name of Charles Krauthammer describes the shifting political climate of the world in his article titled, ``The Authoritarian Temptation'' (November 8, 2019), excerpted from ``The Point of it All,'' Krauthammer's posthumous novel. Krauthammer begins by recalling the late twentieth century $-$ most importantly the fall of the Soviet Union $-$ further through the article, he explains how the whole west has been, from the peak of history (the late twentieth century, in Krauthammer's opinion), progressing to a somewhat more Eastern style of conservative authoritarianism. The author transitions in order to comment on the political world climate, and to question whether America's founding values may be upheld within such a system. As a result, Krauthammer's article may attract readers from all over the globe, especially readers that seek to dive into contemporary politics; he connects with the audience through his transitions and memories of the early twentieth century. 

\end{enumerate}
\end{justify}
\newpage

\begin{center}
 William Safire $-$ \href{https://www.nytimes.com/2009/07/24/opinion/24safire}{Article 3} Pr\'ecis
\end{center}
\begin{enumerate}
    \setcounter{enumi}{2}

  \item William Safire, a political columnist, recalled the fiery Kitchen Debates in his article titled, ``The Cold War's Hot Kitchen,'' that was released exactly 50 years after the Kitchen Debates on July 23, 2009. Safire describes the events that took place at Sokolniki park and his experience while there; as a finale, he concluded that he met someone who he would later find out was the one and only Leonid Brezhnev. The article itself was not argumentative; however, it is evident that the author wrote this article in order to remind and inform the reader of the events that perspired 50 years prior. Therefore, the author connects with the reader by giving a quick history lesson to any possible reader.

\end{enumerate}
\end{justify}
\newpage

\begin{center}
 William Safire $-$ \href{}{Article 4} Pr\'ecis
\end{center}
\begin{enumerate}
    \setcounter{enumi}{3}

  \item 

\end{enumerate}
\end{document}

